---
title: "Interterm"
author: "Katherine Li"
date: "10/16/2019"
output: html_document
---
```{r}
library(tidyverse)
library(ggplot2)
wine <- read_csv('winemag-data-130k-v2.csv')
```

```{r}
winetop <- wine %>%
  group_by(variety) %>%
  summarise(number = n())%>%
  arrange(desc(number))

wine %>%
  filter(variety == 'Pinot Noir' | variety == 'Chardonnay' | variety == 'Cabernet Sauvignon' | variety == 'Red Blend' | variety == 'Bordeaux-style Red Blend' | variety == 'Riesling' | variety == 'Sauvignon Blanc'| variety == 'Syrah' | variety == 'Rosé' | variety == 'Merlot' ) %>%
  filter(is.na(price) != TRUE) %>%
  group_by(variety) %>%
  summarize(avg_price_by_variety=mean(price)) %>%
  arrange(desc(avg_price_by_variety)) %>%
  ggplot(.,mapping=aes(variety, avg_price_by_variety)) +
  geom_bar(stat="identity", fill="darkred") +
  scale_y_continuous("Average Price ($)", breaks=seq(0,60, by=10))+
  ggtitle("Average Price per Bottle",
          subtitle = "Top 10 Varieties") +
  theme_grey() +
  coord_flip() +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.title.y = element_blank())
  
```

```{r}
winenewnew <- wine %>%
  filter(variety == 'Pinot Noir' | variety == 'Chardonnay' | variety == 'Cabernet Sauvignon' | variety == 'Red Blend' | variety == 'Bordeaux-style Red Blend' | variety == 'Riesling' | variety == 'Sauvignon Blanc'| variety == 'Syrah' | variety == 'Rosé' | variety == 'Merlot' ) %>%
  filter(is.na(points) != TRUE) %>%
  group_by(variety) %>%
  summarize(avg_point_by_variety=mean(points)) %>%
  arrange(desc(avg_point_by_variety)) %>%
  ggplot(.,mapping=aes(variety, avg_point_by_variety)) +
  geom_bar(stat="identity", fill="darkblue") +
  scale_y_continuous("Average Rating", breaks=seq(0,60, by=10))+
  ggtitle("Average Rating per Bottle",
          subtitle = "Top 10 Varieties") +
  theme_grey() +
  coord_flip() +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.title.y = element_blank())